Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-08-10 docs/paper/paper.tex
IEEE formatted

\title{\hl{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor
}}

@@

\begin{table*}
	\centering
	\caption{Details of ANN models}
	\begin{tabular}{l|l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} & \textbf{Regressor} \\\hline
		Hidden layers & 5 & 5 & 5 \\
		Neurons in hidden layers & $ 128 $ & $2^{layer\_index} \times 32$ & 50 \\
		Batch size & 32 & 32 & 48 \\
		Activation function & ReLU & Leaky ReLU & ReLU \\
		Optimizer & Adam \cite{kingma2014adam} & Adam & Adam \\
		Input normalization & None & None & None \\
		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
		Loss function & $-Critic(generated)$ & $Critic(gen) - Critic(col) + Penalty_{gradient}$ & MSE \\
	\end{tabular}
	\label{tbl:anndetails}
\end{table*}

>>>>

\title{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor}

@@

\begin{table*}
	\centering
	\caption{Details of ANN models}
	\begin{tabular}{l|l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} & \textbf{Regressor} \\\hline
		Hidden layers & 5 & 5 & 5 \\
		Neurons in hidden layers & $ 128 $ & $2^{layer\_index} \times 32$ & 50 \\
		Batch size & 32 & 32 & 48 \\
		Activation function & ReLU & Leaky ReLU & ReLU \\
		Optimizer & Adam \cite{kingma2014adam} & Adam & Adam \\
		Input normalization & None & None & None \\
		Layer normalization & None & Batch \cite{ioffe2015batch} & Batch \\
		Loss function & $-Critic\left[gen\right]$ & $Critic\left[gen\right] - Critic\left[col\right] + Penalty_{grad}$ & MSE \\\hline
		\multicolumn{4}{l}{gen: generated, col: collected, grad: gradient}
	\end{tabular}
	\label{tbl:anndetails}
\end{table*}
